---
title: "Figure 2 draft"
output: html_document
---

This file relies on having output files from Ass_3.R in your environments: df `combo` and df `precip_final`.
```{r, echo=FALSE}
library(tidyverse)
library(fixest)
library(here)
library(sf)
library(lubridate)
```

No time lag, all countries
```{r}
# No time lags
reg_p2 <- fixest::feols(total ~ poly(yearly_prec, 2, raw=TRUE) | country + year, data = combo)

# Create bootstrapped samples
coefs <- matrix(nrow=1000,ncol=2)
ll = dim(combo)[1]
for (i in 1:1000)  {
  samp <- sample(1:ll,size=ll,replace=T)  
  newdata = combo[samp,]
  mod1 <- feols(total ~ poly(yearly_prec, 2, raw=TRUE) | country + year, data = newdata) 
  coefs[i,] <- coef(mod1)
}
x <- 9:4304
# Create confidence intervals
boots <- matrix(nrow=1000,ncol=length(x))
for (i in 1:1000) {
  yy <- x*coefs[i,1] + x^2*coefs[i,2]   # as before
  yy <- yy - yy[x=967]  # as before
  boots[i,] <- yy  # save these to the boots matrix
}
confint <- apply(boots,2,function(x) quantile(x,probs=c(0.05,0.5,0.95))) 

# Plot bootstrapped median and confidence intervals
plot(1,xlim=c(0,4305),ylim=c(-2,2),las=1,xlab="Annual precipitation, mm",ylab="Change in fragility index")
polygon(c(x,rev(x)),c(confint[1,],rev(confint[3,])),col="grey80",border = NA) + abline(h=0)

yy = x*reg_p2$coefficients[1] + x^2*reg_p2$coefficients[2]  
yy = yy - yy[x=967]
lines(x,yy,col="blue",lwd=2)
```
One time lag, all countries
```{r}
# One time lag
reg_p3 <- fixest::feols(total ~ poly(yearly_prec, 2, raw=TRUE) + poly(yearly_prec_lag1, 2, raw=TRUE) | country + year, data = combo)

# Create bootstrapped samples
coefs <- matrix(nrow=1000,ncol=4)
ll = dim(combo)[1]
for (i in 1:1000)  {
  samp <- sample(1:ll,size=ll,replace=T)  
  newdata = combo[samp,]
  mod1 <- feols(total ~ poly(yearly_prec, 2, raw=TRUE) + poly(yearly_prec_lag1, 2, raw=TRUE) | country + year, data = newdata) 
  coefs[i,] <- coef(mod1)
}
x <- 9:4304
# Create confidence intervals for on-year 
boots <- matrix(nrow=1000,ncol=length(x))
for (i in 1:1000) {
  yy <- x*coefs[i,1] + x^2*coefs[i,2]   # as before
  yy <- yy - yy[x=967]  # as before
  boots[i,] <- yy  # save these to the boots matrix
}
confint <- apply(boots,2,function(x) quantile(x,probs=c(0.05,0.5,0.95))) 

# Create confidence intervals for lag 
boots_lag1 <- matrix(nrow=1000,ncol=length(x))
for (i in 1:1000) {
  yy <- x*coefs[i,3] + x^2*coefs[i,4]   # as before
  yy <- yy - yy[x=967]  # as before
  boots_lag1[i,] <- yy  # save these to the boots matrix
}
confint_lag1 <- apply(boots_lag1,2,function(x) quantile(x,probs=c(0.05,0.5,0.95))) 

# Plot bootstrapped median and confidence intervals
plot(1,xlim=c(0,4305),ylim=c(-2,2),las=1,xlab="Annual precipitation, mm",ylab="Change in fragility index")
polygon(c(x,rev(x)),c(confint[1,],rev(confint[3,])),col="grey80",border = NA) + abline(h=0)

polygon(c(x,rev(x)),c(confint_lag1[1,],rev(confint_lag1[3,])),col="grey60",border = NA) + abline(h=0)

yy = x*reg_p3$coefficients[1] + x^2*reg_p3$coefficients[2]  
yy = yy - yy[x=967]
lines(x,yy,col="blue",lwd=2)

yy = x*reg_p3$coefficients[3] + x^2*reg_p3$coefficients[4]  
yy = yy - yy[x=967]
lines(x,yy,col="red",lwd=2)
```

This chunk is the specification for figure_2()
```{r}
#Produce our figure 2 with two lags
figure_2 <- function(d) {
  max_rainfall <- round(max(d$yearly_prec))
  min_rainfall <- round(min(d$yearly_prec))
  mean_rainfall <- mean(d$yearly_prec)
  reg_p4 <- fixest::feols(total ~ poly(yearly_prec, 2, raw=TRUE) + poly(yearly_prec_lag1, 2, raw=TRUE) + poly(yearly_prec_lag2, 2, raw=TRUE) | country + year, data = d)
  
  # Create bootstrapped samples
  coefs <- matrix(nrow=1000,ncol=6)
  ll = dim(d)[1]
  for (i in 1:1000)  {
    samp <- sample(1:ll,size=ll,replace=T)  
    newdata = d[samp,]
    mod1 <- feols(total ~ poly(yearly_prec, 2, raw=TRUE) + poly(yearly_prec_lag1, 2, raw=TRUE) + poly(yearly_prec_lag2, 2, raw=TRUE) | country + year, data = newdata) 
    coefs[i,] <- coef(mod1)
  }
  x <- min_rainfall:max_rainfall
  # Create confidence intervals for on-year 
  boots <- matrix(nrow=1000,ncol=length(x))
  for (i in 1:1000) {
    yy <- x*coefs[i,1] + x^2*coefs[i,2]   # as before
    yy <- yy - yy[x=mean_rainfall]  # as before
    boots[i,] <- yy  # save these to the boots matrix
  }
  confint <- apply(boots,2,function(x) quantile(x,probs=c(0.025,0.5,0.975))) 
  
  # Create confidence intervals for lag1 
  boots_lag1 <- matrix(nrow=1000,ncol=length(x))
  for (i in 1:1000) {
    yy <- x*coefs[i,3] + x^2*coefs[i,4]   # as before
    yy <- yy - yy[x=mean_rainfall]  # as before
    boots_lag1[i,] <- yy  # save these to the boots matrix
  }
  confint_lag1 <- apply(boots_lag1,2,function(x) quantile(x,probs=c(0.025,0.5,0.975))) 
  
  # Create confidence intervals for lag2 
  boots_lag2 <- matrix(nrow=1000,ncol=length(x))
  for (i in 1:1000) {
    yy <- x*coefs[i,5] + x^2*coefs[i,6]   # as before
    yy <- yy - yy[x=mean_rainfall]  # as before
    boots_lag2[i,] <- yy  # save these to the boots matrix
  }
  confint_lag2 <- apply(boots_lag2,2,function(x) quantile(x,probs=c(0.025,0.5,0.975))) 

  # Plot bootstrapped median and confidence intervals
  par(mfrow=c(1,2))
  plot(NULL,xlim=c(min_rainfall, max_rainfall), ylim=c(min(confint_lag1, confint, confint_lag2), max(confint, confint_lag1, confint_lag2)), las=1,xlab="Annual precipitation, mm",ylab="Change in fragility index")
  polygon(c(x,rev(x)),c(confint[1,],rev(confint[3,])),col=rgb(90, 17, 173, 50, max=255),border = NA) + abline(h=0)
  
  
  
  yy = x*reg_p4$coefficients[1] + x^2*reg_p4$coefficients[2]  
  yy = yy - yy[x=mean_rainfall]
  lines(x,yy,col=rgb(90, 17, 173, max=255),lwd=2)
  
  
  plot(NULL,xlim=c(min_rainfall, max_rainfall),ylim=c(min(confint_lag1, confint, confint_lag2), max(confint, confint_lag1, confint_lag2)),las=1,xlab="Annual precipitation, mm", ylab=NA)
  
  polygon(c(x,rev(x)),c(confint_lag1[1,],rev(confint_lag1[3,])),col=rgb(81, 237, 208, 50, max=255),border = NA) + abline(h=0)
  polygon(c(x,rev(x)),c(confint_lag2[1,],rev(confint_lag2[3,])),col=rgb(227, 98, 121, 50, max=255),border = NA) + abline(h=0)
  
  yy = x*reg_p4$coefficients[3] + x^2*reg_p4$coefficients[4]  
  yy = yy - yy[x=mean_rainfall]
  lines(x,yy,col=rgb(81, 237, 208, max=255),lwd=2)
  
  yy = x*reg_p4$coefficients[5] + x^2*reg_p4$coefficients[6]  
  yy = yy - yy[x=mean_rainfall]
  lines(x,yy,col=rgb(227, 98, 121, max=255),lwd=2)
  return(reg_p4)
}
```


Two time lags, all countries
```{r}
figure_2(combo)
```

Subsetting by 2006-2020 mean FSI
```{r}
mean_fsi <- summarize(group_by(combo, country), mean=mean(total))
# Mean: 70.13
# Median: 75.06
above_median <- filter(mean_fsi, mean>75.06)$country
at_below_median <- filter(mean_fsi, mean<=75.06)$country
first_quart <- filter(mean_fsi, mean<=54.70)$country
second_quart <- filter(mean_fsi, mean<=75.06 && mean > 54.70)$country
third_quart <- filter(mean_fsi, mean>75.06 && mean < 86.04)$country
fourth_quart <- filter(mean_fsi, mean>86.04)$country
```

Somewhat interesting difference in results when comparing more fragile to less fragile countries overall
```{r}
figure_2(filter(combo, country %in% above_median))
```
```{r}
figure_2(filter(combo, country %in% at_below_median))
```

```{r}
figure_2(filter(combo, country %in% first_quart))
```
```{r}
figure_2(filter(combo, country %in% fourth_quart))
```

Subsetting by rainfall
```{r}
mean_prec <- summarize(group_by(combo, country), mean=mean(yearly_prec))
# Mean: 970.92
# Median: 806.32
above_median_p <- filter(mean_prec, mean>806.32)$country
at_below_median_p <- filter(mean_prec, mean<=806.32)$country
first_quart_p <- filter(mean_prec, mean<=473.8)$country
second_quart_p <- filter(mean_prec, mean<=806.32 && mean > 473.8)$country
third_quart_p <- filter(mean_prec, mean>806.32 && mean <= 1292.35)$country
fourth_quart_p <- filter(mean_prec, mean>1292.35)$country
```

No new significant results when comparing wettest 25% to driest 25% of countries
```{r}
figure_2(filter(combo, country %in% fourth_quart_p))
```
```{r}
figure_2(filter(combo, country %in% first_quart_p))
```
No new significant results when comparing wetter vs drier half of world
```{r}
figure_2(filter(combo, country %in% at_below_median_p))
```
```{r}
figure_2(filter(combo, country %in% above_median_p))
```

Subsetting continent (no new significant results)
```{r}
africa <- filter(precip_final, CONTINENT=="Africa")$SOVEREIGNT
s_america <- filter(precip_final, CONTINENT=="South America")$SOVEREIGNT
n_america <- filter(precip_final, CONTINENT=="North America")$SOVEREIGNT
asia <- filter(precip_final, CONTINENT=="Asia")$SOVEREIGNT
europe <- filter(precip_final, CONTINENT=="Europe")$SOVEREIGNT
oceania <- filter(precip_final, CONTINENT=="Oceania")$SOVEREIGNT
```

```{r}
figure_2(filter(combo, country %in% africa))
```

```{r}
figure_2(filter(combo, country %in% asia))
```

```{r}
figure_2(filter(combo, country %in% n_america))
```

```{r}
figure_2(filter(combo, country %in% oceania))
```

```{r}
figure_2(filter(combo, country %in% s_america))
```

By income
```{r}
low_income <- filter(precip_final, INCOME_GRP=="5. Low income")$SOVEREIGNT
high_income <- filter(precip_final, INCOME_GRP=="1. High income: OECD")$SOVEREIGNT
```

Pretty interesting result here
```{r}
figure_2(filter(combo, country %in% low_income))
```

```{r}
figure_2(filter(combo, country %in% high_income))
```



